\textit{MSF: Modulated Sub-graph Finder}

### 2018-04-10 MSF_Paper_FA.tex
Supplement removed
revised the text untill Comparison

High throughput techniques such as RNA-seq or microarray analysis have
proven to be invaluable for the characterization of global
transcriptional gene activity changes due to external stimuli or
diseases. Differential gene expression analysis (DGEA) is the first
step in the course of data interpretation, typically producing lists
of of dozens to thousands of differentially expressed genes. To
further guide the interpretation of these lists, different pathway
analysis approaches have been developed. Most (\TODO{all?}) of which
classify genes into set of genes, i.e. a pathway, which do interact
with each other function in a common biological process. Regardless of
technical differences, all these methods do not properly account for
cross talk between different pathways and rely on binary
classification into differentially expressed gene and unaffected genes
based on an arbitrarily set p-value cut-off.

To overcome this limitation, we developed a novel approach to identify
concertedly modulated sub-graphs in the global cell signaling network,
based on the DGEA results of all genes tested. Thereby, expression
patterns of genes are integrated according to the topology of their
interactions and allow potentially to read the flow of information
from the perturbation source to the effectors. The described software,
named \texttt{Modulated Sub-graph Finder} is freely available at
\url{https://github.com/MariamFarman/Modulated-SubGraph-Finder}.

@@

Differentially expressed genes, Pathway analysis, Combining \textit{p}-value, Cell signaling network, Modulated Sub-graphs

@@

Well established resources for pathway annotation are KEGG (Kyoto
Encyclopedia of Genes and Genomes)\cite{Kegg} and
Reactome~\cite{Reactome}. KEGG pathways is a branch of KEGG database
that has a collection of manually drawn pathway maps representing the
molecular interaction, reaction and relation networks of cellular
functions. Similarly, Reactome is an open-source, manually curated,
peer-reviewed database for signaling and metabolic molecules with
their interactions formed into different biological pathways for
nineteen species~\cite{Reactome}. Both provide predefined pathways
which are sets of genes and their interactions categorized into
functional units. Starting from a gene interaction network, genes are
labeled according their role in a specific biological process. In this
sense a particular gene can be assigned to different pathways. E.g.,
the human gene STAT1 is associated with 24 different pathways in the
pathway annotation curated by
KEGG~\footnote{\url{http://www.genome.jp/dbget-bin/www_bget?hsa:6772}}
and in 12 different pathways in the Reactome data
base~\footnote{\url{http://www.reactome.org/content/detail/R-HSA-629622}}.
Although carefully produced, the assignment of genes to those
predefined pathway unites can be considered to be subjective to some
degree and suffers from observatinal bias (\TODO{citation needed}).

Existing pathway-based analysis approaches use different research
designs, which can be categorized into ORA (Over-representation
analysis), FCS (Functional class scoring) and pathway topology based
methods. All of which aim in finding in a subset of genes, e.g.,
significantly differentially expressed genes, genes associated with a
certain pathway more often than expected given the total set of
examined genes, e.g. the genome background.  ORA is the first and the
most basic method of pathway analysis. It uses a DEG list with user
defined cut-off for the log-fold change and \textit{p}-value (most
commonly using absolute log-fold change $\geq$ 2 and \textit{p}-value
$\leq$ 0.05). Subsequently, sets of genes associated with annotated
pathways are tested for being over-represented in the set of DEGs. To
this end, hyper-geometric distribution, chi-square tests, binomial
probability or the Fisher’s exact test are used. Thereby the
information of the topology of genes in the pathways are
ignored~\cite{Bayer}. Furthermore, ORA assumes that the biological
pathways are independent of each other and ignores the fact that they
cross-talk and overlap~\cite{Khatri2012,Campos}.

Unlike ORA, FCS has no artificial cut-off to define DEG list. FCS
works in three step, first it calculates the gene-level statistics
including correlation of molecular measurements using differential
expression of individual genes, ANOVA, t-test and Z-score. In the
second step the statistics of individual genes in a pathway are
transformed to an individual pathway-level statistic commonly using
Kolmogorov-Smirnov statistic, mean or median. Finally the statistical
significance of the pathway-level statistics is assessed. Although FCS
covers some of the limitations from ORA, it still lacks the topology
of genes in a pathway, cross-talk and overlap of the
pathways~\cite{Khatri2012,Campos}. Pathway topology based methods are
similar to FCS except that they consider the topology of each gene
during the gene-level statistics but still are unable to link
different pathways~\cite{Khatri2012}.

On these grounds we propose a novel approach to make use of the rich
pathway annotation resources available to gain additional functional
insights from basic DGEA. To this, we start with the presupposition
that expression of neighboring genes within a functional pathway are
not independent from each other. Rather, they are often regulating
each others expression or are part of the same
regulon~\cite{Michalak}. We understand that the categorization of
links between genes into labeled pathways is often an arbitrary one,
given the extensive cross talk between different pathways. Although
these categories have proven to be useful in many situations, they
force a certain perspective onto the interpretation of novel
data. Based on these two principles, we aim to find sub-graphs of
connected genes within cell signaling network which exhibit as a whole
significant differential expression changes. As input, information on
functional links between genes provided by e.g. KEGG or Reactome and
information on the differential expression status of single genes
resulting from a DGEA, are required. As a result the analysis returns
sub-graphs and their joint confidence scores, reflecting how the
perturbation is migrated through the network. Furthermore, the entry
points of perturbation in the networks and overlap with conventional
pathway categories are returned. All of this can be helpful to
understand the cause and effect of a stimulus and might inform about
potential points of intervention. The proposed algorithm was
implemented as a java program, which was named \texttt{Modulated Sub-graph
Finder} (abbreviated \texttt{MSF}). \texttt{MSF} can help transform the
information obtained from DGEA into understandable knowledge of signal
transduction of genes and thereby being a valuable complement to existing
pathway based methods. \texttt{MSF} is freely accessible on github.

@@

To reduce the complexity to score all possible connected sub-graphs
\texttt{MSF} applies a four steps heuristic as described in the
following. The proceeding identification of modulated sub-graphs from
a network by \texttt{MSF} is presented as a graphical pseudo code  in
Fig.~\ref{fig:pseudocodemsf}.

@@

After detection and extension of the modulated sub-graphs, they are
tested if combined sub-graph score is better than on their own. The
merging of the two sub-graphs is done by depth first search. If the
two sub-graphs merge with the connector of at most N genes (default
two genes) and the combined \textit{p}-value of the merged sub-graph
including the bridging genes in between is less than the individual
\textit{p}-values of the two sub-graphs, the two sub-graphs are merged
together to one big modulated sub-graph. This step is
repeated iteratively until no sub-graphs could be merged.\newline

@@

In a last post processing step \texttt{MSF} identifies the trigger
points of the modulated sub-graphs. These trigger genes are the
sources of the sub-graphs with only outgoing edges. These genes can be
interpreted as the possible entry points of perturbation from where
the stimulus causes downstream effects. In the same spirit the most
downstream genes of the modulated sub-graph are identified and defined
as sinks. Sinks can be interpreted as the effectors where the
integrated information within the signal transduction network is set
to action. Due to circular loops not all sub-graphs must have sources or
sinks.

@@

To demonstrate its usefulness \texttt{MSF} is applied to RNAseq data
set of primary human monocyte-derived macrophages (MDMs) infected with
Ebola virus (GSE84188)~\cite{Olejnik}. Ebola Virus (EBOV) belongs to
the Filoviridea family; filamentous, enveloped and single stranded RNA
viruses. EBOV causes hemorrhagic fever in humans, inducing the host
innate and adaptive immune response to be unable to control virus
infection~\cite{Prins}. Until now there are no approved antiviral
drugs for the treatment of Ebola virus infection~\cite{Konde,Rhein}.
The initial targets of EBOV are the macrophages and dendritic immune
cells~\cite{Falasca,Rhein}. EBOV inhibits the critical innate immune
response of the host, which includes the activation of alpha/beta
interferon (IFN-$\alpha / \beta$)~\cite{Prins,Konde,Cardenas}. It has been proposed
that IFN-$\alpha / \beta$ should be tested against Ebola for its
antiviral activity through clinical trials~\cite{Konde}. Since the data was most recent and the  infection was carried out in human macrophages, it helped us comprehend the innate immune response of host. The aim of
testing this data with \texttt{MSF} was to identify the
modulated sub-graphs and check if \texttt{MSF} is able to identify the
IFN-$\alpha / \beta$ gene as one of the sources.

EBOV infection count data was downloaded from GEO
(GSE84188). Differential gene expression analysis was performed on the
count data with edgeR package (version 3.4.2)~\cite{edgeR}. The DEG
analysis results generated by edgeR were used as input for \texttt{MSF}. The
EBOV infection experiments describe the course of infection at three time-points 6, 24 and 48 hour post
infection (hpi). For the earliest time point at 6 hpi, five modulated sub-graphs were
identified with 41, 107, and 18 genes. Two of the five sub-graphs were less than 4 genes long. Most of the genes part of the sub-graphs were cytokines, chemokines
(CXCL10, CCL8) and Interleukin genes (IL6, IL27, IL23) which serve as
a subset of CD4+ T helper cells. IFNB1 and IFNA1 were both identified
as two of the possible sources. Most of the sources identified by
\texttt{MSF} were type~I interferon induced genes. At 24 hpi nine
modulated sub-graphs were identified with four main sub-graphs consisting of 38, 85, 148 and 167 genes. IFNA1 was identified as one of
the sources in the most significantly modulated sub-graph. For the last time-point 48 hpi, eleven modulated sub-graphs were identified. Eight of the sub-graphs were less than seven genes and main sub-graphs had 39, 71 and 210 genes. IFNB1 and IFNA1 were
identified as the two sources out of the possible sources.

@@

\subsection*{Modulated sub-graphs at 6 hpi}

 Three main modulated sub-graphs identified by \texttt{MSF} at 6 hpi
 are shown in Fig.~\ref{fig:Sub-graph6hpi}. It shows two forms of graphs, one graph has different colored nodes as
 genes associated to different KEGG pathways. The KEGG
 association and visualization on the modulated sub-graphs was done
 using StringApp~\cite{StringApp} in Cytoscape~\cite{Cyto}. StringApp can retrieve functional enrichment for Gene Ontology terms, KEGG Pathways, and protein domains for a user-specified network. The other graph is a flow chart, that
 unveils how more than one stimulus coincides to prevent the
 progression of infection. Sub-graph 1 shows toll-like receptor,
 cytokine, chemokine and jak-stat genes leading to TNF and eventually
 going into apoptosis. From one end  of sub-graph 2, Extra-cellular matrix (ECM)
 receptor interaction genes are modulated, which are suggested to be in interaction
 with Ebola glycoprotein (GP)~\cite{Veljkovic}. ECM receptor, Focal
 adhesion and P13k-Akt signaling genes are the sources from this end of
 the sub-graph, with P13k-Akt signaling going to FoxO signaling which
 eventually leads to cell cycle, that at later time-points is
 seen to be disrupted. From the other end of sub-graph 2 toll-like recpetor
 combined with cytosolic DNA sensing and cytokine-chemokine signaling
 activates Jak-stat which leads to the start of apoptosis with a
 few apoptosis genes being modulated. Cytokine is also seen to sink
 into natural killer mediated cytotoxicity. Sub-graph 3 shows how some
 of the cytokine and chemokine genes activate the natural killer
 mediated cytotoxicity and apoptosis.

 To assess the robustness and stability of our method, Poisson
 distributed noise was added to the read counts of the three time-points. Then DGEA was
 carried out on the disturbed data with the same parameters as for the
 native data using edgeR, followed by analysis with \texttt{MSF}. This procedure was carried out 100 times
 and every time the genes from the sub-graphs identified from noisy
 data were compared to the genes of sub-graphs identified from the
 native data. This was also done for the DEG obtained for each run, a
 cutoff was used to compare the retrieved DEG from noisy data to the
 native data.  The robustness of \texttt{MSF} and the DEG analysis for
 the time-point 6, 24, and 48 hpi are shown in Fig.~\ref{fig:DEGvsMSF}. We were very stringent in
 adding noise to the counts, which could be seen by the DEG analysis
 robustness. For the last time-point (48h~p.i.) 84~\% genes of the
 sub-graphs from native data were retrieved, for 24~h~p.i. recall rate was
 79~\%. Robustness was 71~\% at 6~h~p.i., this could be due to that the
 infection merely started and the signal transdcution was weak as
 compared to the later time-points.

 To test \texttt{MSF's} correctness simulation was also conducted. For each time-point, one \texttt{MSF} identified sub-graph was selected and using simulation random graph was generated with the same number of genes as the sub-graphs utilizing the same interaction file. The simulation identified sources were counted from the simulated sub-graph. The objective
 was to find less sources in the simulated sub-graphs than observed in the real sub-graphs identified by
 \texttt{MSF}. Simulation results showed a chance of $<$10$\%$
 of the 1000 random sub-graphs generated to get more sources than observed.

@@

\subsection*{Supplementary Material}

The supplementary file contains tables of comparison between
\textbf{MSF} identified sub-graph gene enrichment with SPIA and
Reactome pathway analysis.

>>>>

High throughput techniques such as RNA-seq or microarray analysis have
proven to be invaluable for the characterization of global transcriptional
gene activity changes due to external stimuli or diseases. Differential
gene expression analysis (DGEA) is the first step in the course of data
interpretation, typically producing lists of of dozens to thousands of
differentially expressed genes. To further guide the interpretation of
these lists, different pathway analysis approaches have been
developed. These tools typically classify genes into set of genes, i.e. a
pathway, which interact with each other and function in a common biological
process. Regardless of technical differences, all these methods do not
properly account for cross talk between different pathways and rely on
binary classification into differentially expressed gene and unaffected
genes based on an arbitrarily set p-value cut-off.

To overcome this limitation, we developed a novel approach to identify
concertedly modulated sub-graphs in the global cell signaling network,
based on the DGEA results of all genes tested. Thereby, expression
patterns of genes are integrated according to the topology of their
interactions and allow potentially to read the flow of information
from the perturbation source to the effectors. The described software,
named \texttt{Modulated Sub-graph Finder} (\texttt{MSF}) is freely available at
\url{https://github.com/MariamFarman/Modulated-SubGraph-Finder}.

@@

Differential gene expression analysis; pathway analysis; combining \textit{p}-value; cell signaling network;

@@

Well established resources for pathway annotation are KEGG (Kyoto
Encyclopedia of Genes and Genomes)\cite{Kegg} and
Reactome~\cite{Reactome}. KEGG pathways is a branch of KEGG database that
hosts a collection of manually drawn pathway maps representing the
molecular interaction, reaction and relation networks of cellular
functions. Similarly, Reactome is an open-source, manually curated,
peer-reviewed database for signaling and metabolic molecules with their
interactions formed into different biological pathways for nineteen
species~\cite{Reactome}. Both provide predefined pathways which are sets of
genes and their interactions categorized into functional units. Starting
from a gene interaction network, genes are labeled according their role in
a specific biological process. In this sense a particular gene can be
assigned to different pathways. E.g., the human gene STAT1 is associated
with 24 different pathways in the pathway annotation curated by
KEGG~\footnote{\url{http://www.genome.jp/dbget-bin/www_bget?hsa:6772}} and
in 12 different pathways in the Reactome data
base~\footnote{\url{http://www.reactome.org/content/detail/R-HSA-629622}}.
Although carefully produced, the assignment of genes to those predefined
pathway unites can be considered to be subjective to some degree and
suffers from observational bias~\cite{schnoes2013biases}.

Existing pathway-based analysis approaches use different research designs,
which can be categorized into ORA (Over-representation analysis), FCS
(Functional class scoring) and pathway topology based methods. All of which
aim in finding in a subset of genes, e.g., significantly differentially
expressed genes, genes associated with a certain pathway more often than
expected given the total set of examined genes, e.g.~the whole genome
background.  ORA is the first and the most basic method of pathway
analysis. It uses a DEG list with user defined cut-off for the log-fold
change and \textit{p}-value (most commonly using absolute log-fold change
$\geq$ 2 and \textit{p}-value $\leq$ 0.05). Subsequently, sets of genes
associated with annotated pathways are tested for being over-represented in
the set of DEGs. To this end, hyper-geometric distribution, chi-square
tests, binomial probability or the Fisher’s exact test are used. Thereby
the information of the topology of genes in the pathways are
ignored~\cite{Bayer}. Furthermore, ORA assumes that the biological pathways
are independent of each other and ignores the fact that they cross-talk and
overlap~\cite{Khatri2012,Campos}.

Unlike ORA, FCS has no artificial cut-off to define DEG list. FCS works in
three step, first it calculates the gene-level statistics including
correlation of molecular measurements using differential expression of
individual genes, ANOVA, t-test and Z-score. In the second step the
statistics of individual genes in a pathway are transformed to an
individual pathway-level statistic commonly using Kolmogorov-Smirnov
statistic, mean or median. Finally the statistical significance of the
pathway-level statistics is assessed. Although FCS covers some of the
limitations from ORA, it still lacks the topology of genes in a pathway,
cross-talk and overlap of the pathways~\cite{Khatri2012,Campos}. Pathway
topology based methods are similar to FCS except that they consider the
topology of each gene during the gene-level statistics but still don't aim
to link different functional pathways~\cite{Khatri2012}.

On these grounds we propose a novel approach to make use of the rich gene
and protein interaction annotation resources available to gain additional
functional insights from basic DGEA. To this, we start with the
presupposition that expression of neighboring genes within a functional
pathway are not independent from each other. Rather, they are often
regulating each others expression or are part of the same
regulon~\cite{Michalak}. We understand that the categorization of links
between genes into labeled pathways is often an arbitrary one, given the
extensive cross talk between different pathways. Although these categories
have proven to be useful in many situations, they force a certain
perspective onto the interpretation of novel data. Based on these two
principles, we aim to find sub-graphs of connected genes within cell
signaling network which exhibit as a whole significant differential
expression changes. This approach differes in two main aspects from common
pathway analysis tools. First, it does not aim to identify functional
pathways enriched in differentially expressed genes, but detects sub-graphs
or branches in a network graph (potentially spanning more than one
functionally grouped pathway) which is coherently modulated. Second, it
aims to improve the DGEA on the gene level, by collecting the information
of neighboring genes, which as a whole might exhibit prominent enough
signal to be called, again as a whole, significantly modulated.

As input, information on functional links between genes provided by
e.g.~KEGG or Reactome and information on the differential expression status
of single genes resulting from a DGEA, are required. As a result the
analysis returns sub-graphs and their joint confidence scores, reflecting
how the perturbation is migrated through the network. Furthermore, the
entry points of perturbation in the networks and overlap with conventional
pathway categories are returned. The output is prepared for convenient
visualisation with the \TODO{StringApp, available as a Cytoscape plug-in.}

All of this can be helpful to understand the cause and effect of a stimulus
and might inform about potential points of intervention. The proposed
algorithm was implemented as a java program, which was named
\texttt{Modulated Sub-graph Finder} (abbreviated
\texttt{MSF}). \texttt{MSF} can help transform the information obtained
from DGEA into comprehensible knowledge of signal transduction of genes and
thereby being a valuable complement to existing pathway based
methods. \texttt{MSF} is freely accessible on github \TODO{which licence?}.

@@

To reduce the complexity to score all possible connected sub-graphs
\texttt{MSF} applies a four steps heuristic as described in the
following. The proceeding identification of modulated sub-graphs from a
network by \texttt{MSF} is presented as a flowchart diagram
(Fig.~\ref{fig:pseudocodemsf}).

@@

After detection and extension of the modulated sub-graphs, they are tested
if combined sub-graphs score better than on their own. The merging of the
two sub-graphs is done by depth first search. If the two sub-graphs merge
with the connector of at most N genes (default two genes) and the combined
\textit{p}-value of the merged sub-graph including the bridging genes in
between is less than the individual \textit{p}-values of the two
sub-graphs, the two sub-graphs are merged together to one big modulated
sub-graph. This step is repeated iteratively until no sub-graphs could be
merged.\newline

@@

In a last post processing step \texttt{MSF} identifies the trigger points
of the modulated sub-graphs. These trigger genes are the sources of the
sub-graphs with only outgoing edges. These genes can be interpreted as the
possible entry points of perturbation from where the stimulus causes
downstream effects. In the same spirit the most downstream genes of the
modulated sub-graph are identified and defined as sinks. Sinks can be
interpreted as the effectors where the integrated information within the
signal transduction network is set to action. Due to circular loops not all
sub-graphs are guaranteed to have sources or sinks.

@@

To demonstrate its usefulness, \texttt{MSF} is applied to an RNAseq data
set of primary human monocyte-derived macrophages (MDMs) infected with
Ebola virus (GSE84188)~\cite{Olejnik}. Ebola Virus (EBOV) belongs to the
Filoviridea family; filamentous, enveloped and single stranded RNA
viruses. EBOV causes hemorrhagic fever in humans, inducing the host innate
and adaptive immune response to be unable to control virus
infection~\cite{Prins}. Until now, there are no approved antiviral drugs
for the treatment of Ebola virus infection~\cite{Konde,Rhein}.  The initial
targets of EBOV are the macrophages and dendritic immune
cells~\cite{Falasca,Rhein}. EBOV inhibits the critical innate immune
response of the host, which includes the activation of alpha/beta
interferon (IFN-$\alpha / \beta$)~\cite{Prins,Konde,Cardenas}. It has been
proposed that IFN-$\alpha / \beta$ should be tested against Ebola for its
antiviral activity through clinical trials~\cite{Konde}. \TODO{I do not get
this sentence: Since the data was most recent and the infection was
carried out in human macrophages, it helped us comprehend the innate
immune response of host}. The aim of testing this data with \texttt{MSF} was
to identify the modulated sub-graphs and check if \texttt{MSF} is able to
identify the IFN-$\alpha / \beta$ gene as one of the sources, and show that
the capability to close ``gaps'' by using information of neighboring genes
is effective.

\TODO{TODO: If MSF is not applied but only significant genes are mapped on
  the reactom data set, into how many sub-graphs would the data fall apart?
  in other words: how many genes are only significant because they are part
  of a significant sub-graph but are not on there own?}

EBOV infection count data was downloaded from GEO (GSE84188). Differential
gene expression analysis was performed on the count data with edgeR package
(version 3.4.2)~\cite{edgeR}. The DEG analysis results generated by edgeR
were used as input for \texttt{MSF}. The EBOV infection experiments
describe the course of infection at three time-points 6, 24 and 48 hour
post infection (hpi). For the earliest time point at 6~hpi, five modulated
sub-graphs were identified with 41, 107, and 18 genes. Two of the five
sub-graphs were less than 4 genes long. Most of the genes part of the
sub-graphs were cytokines, chemokines (CXCL10, CCL8) and Interleukin genes
(IL6, IL27, IL23) which serve as a subset of CD4+ T helper cells. IFNB1 and
IFNA1 were both identified as two of the possible sources. Most of the
sources identified by \texttt{MSF} were type~I interferon induced genes. At
24~hpi nine modulated sub-graphs were identified with four main sub-graphs
consisting of 38, 85, 148 and 167 genes. IFNA1 was identified as one of the
sources in the most significantly modulated sub-graph. For the last
time-point 48~hpi, eleven modulated sub-graphs were identified. Eight of
the sub-graphs were less than seven genes and main sub-graphs had 39, 71
and 210 genes. IFNB1 and IFNA1 were identified as the two sources out of
the possible sources.

\subsection*{Modulated sub-graphs at 6~hpi}

 Three main modulated sub-graphs identified by \texttt{MSF} at 6~hpi are
 shown in Fig.~\ref{fig:Sub-graph6hpi}. The gene based graphs on the right
 hand side, represent the immediate output of the \texttt{MSF}-analysis,
 visualised by StringApp~\cite{StringApp} in Cytoscape~\cite{Cyto}. Each
 node represents a gene part of a modualted sub-graph, whereby the
 associated colors code the functional annotation deduced from KEGG
 Pathways. The crosstalk between the pathways and also the mutliple
 employment of many genes is evident. The more schematic drawing on the
 right side represents the effortlessly deduced flow of information between
 the sensors and effectors in this particular example.

 In more detail, sub-graph~1 (top) shows how the activation of toll-like
 receptor, cytokine, chemokine and jak-stat genes lead via TNF into
 apoptosis. The next significant sub-grap (sub-graph~2: middle) reveals how
 information from the Extra-cellular matrix (ECM) receptor, which are
 reported to interact with Ebola glycoprotein (GP)~\cite{Veljkovic},
 chemokines and cytokines, and cytosolic DNA sensing, is integrated into
 again modulation of apoptosis pathway. Eventually, sub-graph~3 (bottom)
 demonstrate how INFA1 and INFB1 modulate once more, via only a few
 intermediat steps, the aptoptotic response of the cell.

 This show cast example might advertise with how little effort complex data
 cat be interpreted, help to apprehend the dynamics of the underlying
 processes and suggest testable hypothesis and potential points of
 intervention.

 To assess the robustness and stability of our method, Poisson distributed
 noise was added to the read counts of the three time-points data set, used
 in the previous analysis. Then DGEA was carried out on the disturbed data
 with the same parameters as for the native data using edgeR, followed by
 analysis with \texttt{MSF}. This procedure was carried out 100 times.
 Every time the genes from the modulated sub-graphs identified from noisy
 data were compared to the genes of sub-graphs identified from the native
 data. This was also done for the DEG obtained for each run, a cutoff
 \TODO{what cutoff?} was used to compare the retrieved DEG from noisy data
 to the native data.  The robustness of \texttt{MSF} and the DEG analysis
 for the time-point 6, 24, and 48~hpi are shown in
 Fig.~\ref{fig:DEGvsMSF}. The procedure how data noise was modeled can be
 considered as rather stringent, which is already reflected limited recall
 rate in the edgeR based DGEA, between \TODO{X and Y~\%}. For
 \texttt{MSF}-analysis the observed median recall rates lay between 71~\%
 (6~hpi) and 84~\% (48~hpi).

 \TODO{This paragraph makes no sense to me:
 To test \texttt{MSF's} correctness simulation was also conducted. For each
 time-point, one \texttt{MSF} identified sub-graph was selected and using
 simulation random graph was generated with the same number of genes as the
 sub-graphs utilizing the same interaction file. The simulation identified
 sources were counted from the simulated sub-graph. The objective was to
 find less sources in the simulated sub-graphs than observed in the real
 sub-graphs identified by \texttt{MSF}. Simulation results showed a chance
 of $<$10$\%$ of the 1000 random sub-graphs generated to get more sources
 than observed.}

@@

@@
